SNIK: Textbook Knowledge on Hospital Information Management as Linked Data

### 2020-07-15 paper.tex
Update triple count including DBpedia links.
Update statistics and wrap its tabulary in a table.

%\usepackage{dcolumn}
%\usepackage{endnotes}
\usepackage{booktabs}
\usepackage{tabulary}
\usepackage{csquotes}
\usepackage{siunitx}
%\usepackage{graphicx}
\usepackage{todonotes}
%\usepackage{natbib} % does not seem to work with ios 1
\renewcommand{\citet}{\cite}% citet is not defined without natbib
\renewcommand{\citep}{\cite}% citep is not defined without natbib
\setlength{\marginparwidth}{2.1cm}% enough space for todonotes
\usepackage{listings}
\usepackage{aurl}
\daurl{bb}{http://www.snik.eu/ontology/bb/}
\daurl{meta}{http://www.snik.eu/ontology/meta/}
\lstset{language=SPARQL,breaklines=true}
\usepackage{cleveref}
\newcommand{\snikversion}{1.0}
\newcommand{\sniktriples}{\num{71852}}
\newcommand{\snikclasses}{\num{2655}}
\newcommand{\snikproperties}{\num{339}}
\newcommand{\sniklinks}{\num{581}}
%%%%%%%%%%% End of definitions

@@

\begin{tabulary}{\columnwidth}{lL}
\toprule
URL		&\url{http://www.snik.eu/ontology}\\
Version		&2018-10-10, \snikversion{}\\
License		&CC BY-NC-SA 4.0\\
SPARQL Endpoint	&\url{http://www.snik.eu/sparql}\\
Visualization	&\url{http://www.snik.eu/graph}\\
RDF Browser	&\url{http://www.snik.eu/ontology}\\
Download	&\url{https://github.com/IMISE/snik-ontology/releases/download/1.0.0/snik.zip}\\
\# Triples	&\sniktriples{}\\
\# Classes	&\snikclasses{}\\
\# Properties	&\snikproperties{}\\
\# Interlinks	&\sniklinks{}\\
%Subontologies	&\url{http://www.snik.eu/ontology/bb}\\
%		&\url{http://www.snik.eu/ontology/ciox,}\\
%		&\url{http://www.snik.eu/ontology/ob}\\
%		&\url{http://www.snik.eu/ontology/he}\\
%		&\url{http://www.snik.eu/ontology/it4it}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}

>>>>

%\usepackage{dcolumn}
%\usepackage{endnotes}
\usepackage{booktabs}
\usepackage{tabulary}
\usepackage{csquotes}
\usepackage{siunitx}
%\usepackage{graphicx}
\usepackage{todonotes}
%\usepackage{natbib} % does not seem to work with ios 1
\renewcommand{\citet}{\cite}% citet is not defined without natbib
\renewcommand{\citep}{\cite}% citep is not defined without natbib
\setlength{\marginparwidth}{2.1cm}% enough space for todonotes
\usepackage{listings}
\usepackage{aurl}
\daurl{bb}{http://www.snik.eu/ontology/bb/}
\daurl{meta}{http://www.snik.eu/ontology/meta/}
\lstset{language=SPARQL,breaklines=true}
\usepackage{cleveref}
\newcommand{\snikversion}{1.0}
\newcommand{\sniktriples}{\num{72046}}
\newcommand{\snikclasses}{\num{2655}}
\newcommand{\snikproperties}{\num{339}}
\newcommand{\sniklinks}{\num{581}}
%%%%%%%%%%% End of definitions

@@

\begin{table}
\caption{Statistics and Details}
\label{tab:namespaces}
\begin{tabulary}{\columnwidth}{lL}
\toprule
URL		&\url{http://www.snik.eu/ontology}\\
Version		&\snikversion{}\\
License		&CC BY-NC-SA 4.0\\
SPARQL Endpoint	&\url{http://www.snik.eu/sparql}\\
LOD Cloud	&\url{https://lod-cloud.net/dataset/snik}\\
Datahub		&\url{https://datahub.io/imise/snik/v/1}\\
Visualization	&\url{http://www.snik.eu/graph}\\
RDF Browser	&\url{http://www.snik.eu/ontology}\\
Download	&\url{https://github.com/IMISE/snik-ontology/releases/download/1.0.0/snik.zip}\\
\# Triples	&\sniktriples{}\\
\# Classes	&\snikclasses{}\\
\# Properties	&\snikproperties{}\\
\# Internal Links	&\num{360}\\
\# Links to HITO  	&\num{260}\\
\# Links to DBpedia 	&\sniklinks{}\\
%Subontologies	&\url{http://www.snik.eu/ontology/bb}\\
%		&\url{http://www.snik.eu/ontology/ciox,}\\
%		&\url{http://www.snik.eu/ontology/ob}\\
%		&\url{http://www.snik.eu/ontology/he}\\
%		&\url{http://www.snik.eu/ontology/it4it}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}
